### 2014-10-07 paper/include/background.tex
wiriten cool stuff on all aproaches, or something.

DRAM is hierarchically organized as in \reffig{fig:dram_orga}. At the top of the hierarchy are the channels that are connected to one or more ranks, each composed of multiple storage arrays called banks. Each channel has individual address, data, and command buses that makes it possible for the channels to operate concurrently. All ranks on one channel can also operate in parallel constrained by the channel bandwidth which is shared among the ranks. Further, the banks within the ranks are also able to operate in parallel, but are constrained by both the shared channel bandwidth and resources shared among the banks.

>>>>

DRAM is hierarchically organized as in \reffig{fig:dram_orga}. At the top of the hierarchy are the channels that are connected to one or more ranks, each composed of multiple storage arrays called banks. Each channel has individual address, data, and command buses that makes it possible for the channels to operate cuncurrently. All ranks on one channel can also operate in parallel constrained by the channel bandwith which is shared among the ranks. Further, the banks within the ranks are also able to operate in parallel, but are constrianed by both the shared channel bandwith and resources shared among the banks.
